% Quick start guide
\documentclass{beamer}

\hypersetup{colorlinks=true}

% \usepackage[colorlinks=true]{hyperref}
\usepackage{natbib}
\usepackage{apalike}
\usepackage{amsthm}
\usepackage{verbatim}

\usetheme{default}
% \usetheme{Madrid}

\newtheorem{probDef}{Definition}
\newtheorem*{probDef*}{Definition}
\newtheorem{claim}{Claim}
\newtheorem*{claim*}{Claim}
\newtheorem*{lemma*}{Lemma}
\newtheorem{probExample}{Example}
\newtheorem{probRule}{Rule}
\newtheorem{probAxiom}{Axiom}
\setbeamertemplate{theorems}[numbered]
\newtheorem{probExercise}{Exercise}

\newtheorem{manualprobRuleinner}{Rule}
\newenvironment{manualProbRule}[1]{%
  \renewcommand\themanualprobRuleinner{#1}%
  \manualprobRuleinner
}{\endmanualprobRuleinner}

\newtheorem{manualprobExampleinner}{Example}
\newenvironment{manualProbExample}[1]{%
  \renewcommand\themanualprobExampleinner{#1}%
  \manualprobExampleinner
}{\endmanualprobExampleinner}

\newcounter{saveenumi}
\newcommand{\seti}{\setcounter{saveenumi}{\value{enumi}}}
\newcommand{\conti}{\setcounter{enumi}{\value{saveenumi}}}
\newcommand{\keepi}{\addtocounter{saveenumi}{-1}\setcounter{enumi}{\value{saveenumi}}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

% Title page details
\title{Bonsai.ML}
\subtitle{Intelligent Experimental Control}
\author{Nicholas Guilbeault and Gon\c{c}alo Lopes and Joaqu\'{i}n Rapela}
\institute{Gatsby Computational Neuroscience Unit\\NeuroGEARS Ltd.}
\date{December 5, 2024}

\AtBeginSection[ ]
{
\begin{frame}{Outline}
    \tableofcontents[currentsection]
\end{frame}
}

\begin{document}

\begin{frame}
	\titlepage
\end{frame}

\begin{frame}{Outline}
    \tableofcontents
\end{frame}

\section{Introduction}

\begin{frame}
    \frametitle{History of Bonsai.ML}

    \begin{itemize}

        \item grant application

        \item developing tools

        \item who cares about Bonsai.ML tools? $\rightarrow$ more focus on
            dissemination

        \item real-time ML

    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Goals of Bonsai.ML}

    \begin{itemize}
        \item allow non-programmers use ML tools,
        \item learn from non-programmers what ML tools are useful for them
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Need for Real-Time and Reactive ML}

    Conventional ML operates on stored datasets. We need real-time ML that
    operates on infinite data stream with time-varying statistical properties.

    If a sensor fails, our inferences need to continue. That is, we need
    reactive ML (e.g., \href{https://rxinfer.ml/}{rx.infer}).
\end{frame}

\begin{frame}
    \frametitle{Bonsai.ML demos}

\end{frame}

\section{Linear Regression}

\begin{frame}
    \frametitle{Linear Regression: Fundamental Concepts}

    \begin{itemize}
        \item main concepts of linear regression
        \item Online Bayesian Linear Regression (can process infinite data streams, but assumes stationarity)
        \item Recursive least squares (can process infinite data streams, and
            does not assume stationarity)
    \end{itemize}

\end{frame}

\begin{frame}
    \frametitle{Linear Regression: Practical}

    Estimation of receptive fields of visual cells from the Allen Institute.

\end{frame}

\input{linearRegression}

\section{Bonsai-Python Integration}

\begin{frame}
    \frametitle{Bonsai-Python Integration: Fundamental Concepts}

    \begin{itemize}
        \item architecture
        \item async/sync regimes
    \end{itemize}

\end{frame}

\begin{frame}
    \frametitle{Bonsai-Python Integration: Practical}

    \begin{itemize}
        \item Bonsai-Python Hello World
        \item Bonsai-Python advanced example
    \end{itemize}

\end{frame}

\section{Linear Dynamical Systems}

\begin{frame}
    \frametitle{Linear Dynamical Systems: Fundamental Concepts}

    Fundamental concepts of LDS.

\end{frame}

\begin{frame}
    \frametitle{Linear Dynamical Systems: Practical}

    Estimation of foraging mice kinematics.

\end{frame}

\section{Hidden Markov Models}

\begin{frame}
    \frametitle{Hidden Markov Models: Fundamental Concepts}

    Fundamental concepts of HMMs.

\end{frame}

\begin{frame}
    \frametitle{Hidden Markov Models: Practical}

    Estimation of behavioral states of foraging mice.

\end{frame}

\section{State-Space Decoders}

\begin{frame}
    \frametitle{State-Space Decoders: Fundamental Concepts}

    Fundamental concepts of state-space decoders.

\end{frame}

\begin{frame}
    \frametitle{State-Space Decoders: Practical}

    Mice position decoding from hippocampal population activity.

\end{frame}

\section{Discussion}

\begin{frame}
    \frametitle{Discussion}

    \begin{itemize}
        \item interactions between experimental and computational
            neuroscientists (documentation)

        \item Bonsai.ML roadmap

            \begin{itemize}

                \item our proposal
                \item suggestions?

            \end{itemize}

        \item suggestions for:

            \begin{itemize}
                \item new ML models to integrate into Bonsai
                \item new applications areas to investigate with Bonsai.ML
            \end{itemize}

    \end{itemize}

\end{frame}

\begin{frame}
    \frametitle{References}

    \tiny{
        \bibliographystyle{apalike}
        \bibliography{probability,informationTheory,machineLearning,gaussianProcesses,latentsVariablesModels,linearDynamicalSystems,numericalMethods}
    }
\end{frame}

\end{document}
