
\begin{frame}
    \frametitle{Dissemination}

    \begin{itemize}[<+->]

        \item we may add excellent machine learning functionality to Bonsai
            that nobody uses, since some knowledge of machine learning is needed
            to use generic machine learning models.

        \item reviewer comment: \emph{by adding machine learning methods
            to Bonsai, you may be doing more harm than good}.

        \item focus on documentation, dissemination and early collaborations.

        \item problem driven or tool driven? I prefer to be problem driven,
            collaborate with experimental scientists using Bonsai.ML to solve
            specific problems, and then disseminate the Bonsai tool plus with
            the example problems we solved together.

        \item we have the privilege of working on one of the most prestigious
            centres for experimental neuroscience. We want to apply our
            Bonsai.ML tools to help them process their data.

        \item or perhaps we should be patient, add excellent ML methods to
            Bonsai, and maybe people will use them.

    \end{itemize}

\end{frame}

\begin{frame}
    \frametitle{Other topics}

    \begin{itemize}

        \item how to disseminate Bonsai.ML?
            \begin{itemize}

                \item distribute methods, with high-quality code,
                    documentation and examples.

                \item publish papers.

                \item collaborate with experimentalists to use Bonsai.ML
                    to tackle interesting neuroscience problems.

                \item train the trainers.

                \item train Bonsai users on basic machine learning topics.

                \item find a killer Bonsai.ML application.

            \end{itemize}

        \item suggestions for Bonsai.ML roadmap?

        \item suggestions for:

            \begin{itemize}
                \item new ML models to integrate into Bonsai
                \item new applications areas to investigate with Bonsai.ML

                    \begin{itemize}

                        \item testing causality of brain activity patterns on
                            behaviour

                        \item online selection of data to save (e.g. cameras)

                        \item Bonsai for online data analysis (e.g., Terry
                            Sejnowski: for very large datasets, retrieval could
                            be very onerous, so you'd better analyse data
                            online).
                    \end{itemize}

            \end{itemize}

    \end{itemize}

\end{frame}

